How to compute the fusion product of MV cycles in type A

### 2021-03-09 draft.tex
minor edits plus commented out nicematrix

Given a coweight $\mu \in P$ and $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix 
% with entries $ (t-s)^{\mu_1}, \dots, (t-s)^{\mu_m}$
% \[
%     \begin{pNiceMatrix}[nullify-dots,xdots/line-style=loosely dotted]
%         (t-s)^{\mu_1} & 0             & \Cdots & 0 \\
%         0             & (t-s)^{\mu_2} & \Ddots & \Vdots \\
%         % 0 & b & a & \Ddots & & \\
%         \Vdots              & \Ddots        & \Ddots & 0 \\
%         % \Vdots & & & & \\
%         0             & \Cdots        &   0    & (t-s)^{\mu_m}
%     \end{pNiceMatrix}
% \]
\[
\begin{bmatrix}
    (t-s)^{\mu_1} \\
    & (t-s)^{\mu_2} \\ 
    & & \ddots \\
    & & & (t-s)^{\mu_m}
\end{bmatrix} 
\]
which we will view in $\GL_m(K) $ for any ring $ K $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ K = \Ks, \CC(t)$). % A: Think R sb K; changed it

@@

\subsection{Affine Grassmannians} %  actors
% To map thick Gr to C is to map a lattice to the points where it isn't trivialzable; doesn't make sense to ask for poles 
% G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
Set $\AA = \AA^1$.

\jcom{I don't think that we need all this about ``formal disc centered at $s$'' below since we now define this in the rings and discs section.}
\acom{Ok.}

\begin{itemize}
    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by 
    $$
    \Gr = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0 \setminus \{0\} $} \} 
    $$
    where $V_0$ is the trivial rank $m$ vector bundle.
    % and $ D_0$ is the formal disc centered at $ 0 \in \PP$.

    We also have a lattice description 
    $$ 
    \Gr = \{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \}\,.
    $$
    % 
    \item For any $ s \in \CC $, 
    % \acom{should it be $\AA$ instead of $\CC$} 
    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
    $$
    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_s \setminus \{s\} $} \}\,.
    $$
    % where $D_s$ is the formal disc centered at $s$ viewed as an element of $\PP$.
    \acom{What about fixing the notation $V_0$ somewhere?}

    We also have a lattice description 
    $$ 
    \Gr_s = \{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \} \,. 
    $$   
    \item The thick affine Grassmannian $\Grth = G(\Kinf)/G(\CC[t])$. % \CC\xT[t^{-1}]
    It is described in modular terms by
    $$
        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \} % (a disc centered at $ \infty$)
    $$
    where $D_\infty$ denotes a disc centered at $ \infty$. 
    % \acom{What is the difference between ``a disc'' and ``the formal disc''} \jcom{No difference.}

    We also have a lattice description 
    $$ 
    \Grth = \{ L \subset  \Kinf^m : \text{ $L$ is a $\CC[t]$-lattice} \}\,.
    $$ % \CC\xT[t^{-1}]^m

@@

    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
    It is described in modular terms by
    % {\small
    $$
    \Grbd = 
    % \begin{aligned}
        \left\{ 
            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \xrightarrow{\sim} V_0 \text{ on } \PP \setminus \{0, s\}  
        \right\} 
    % \end{aligned}
    $$%}

    The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by \rcom{why do we have the $s\ne 0$ restriction here}
    % 
    $$ 
    \Gr_{0,s} = G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
    $$
    % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
    % \jcom{Yes, that is one reason.  But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).  For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
    % \acom{lol}

    We also have a lattice descriptions 
    % {\small
    \begin{gather*}
    \Grbd = 
    \{ (L,s) :
    % s\in\AA,\,
    % L \subset  \CC(t)^m, s \in \AA 
    \text{$L \subset  \CC(t)^m$ is a $\CC[t]$-lattice trivial at any $ a \ne 0, s$} \} \\
    % , $L$ is 
     \Gr_{0,s} = 
    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}
    \end{gather*}%}
    \acom{We do not consistently specify where $s$ is in these definitions}
    % \acom{$s\in\CC$ should be $s\in\AA$?}
    % \jcom{Sorry I was very consistent about $ \CC$ vs $\AA$.  Which do you prefer?}
    % 
    \item The positive parts $ \Gr^+$ and ${\Grth}^+$ of the affine Grassmannian and of the thick affine Grassmannian resp.\ are defined as 
    % and of the thick affine Grassmannian ${\Grth}^+$ is defined as
    $$
    \Gr^+ = (M_m(\cO) \cap G(\cK)) / G(\cO) \quad {\Grth}^+ = (M_m(\CC[t]) \cap G(\Kinf) / G(\CC[t]) % \CC\xT[t^{-1}] missed a spot  
    $$
    % \acom{What is $M_m$?} \jcom{The space of matrices.  I added it to the beginning of section 2.}

    In modular terms, $\Gr^+$ (resp. ${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow V_0 $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp. over $ \PP$).

    In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the (relevant?) standard lattice. 
    % \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.  But I would like to leave the terminology ``trivial at $ a$'' is that ok, or should we write ``standard at $a$''.} 
    % \acom{Oh, I don't know.. is trivialized at $a$? is standardized at $a$? Maybe standard at $a$ is better.. Man I never thought about this interchangeable lingo.} 
    % lattice $ L_0(\cO)$ (resp. $L_0(\CC[t])$). % , i.e. $ L \subseteq L_0$.
\end{itemize}
% \acom{enumerate the points for now}
These different versions of the affine Grassmannian are related as follows.

\begin{enumerate}
    \item First there is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \cK \cong \Ks$.
    \item Second, we have a map from the two point BD affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
    % $$ \Grbd \rightarrow \Grth $$ 
    which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by
    $$
    G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])
    $$
    % \acom{Permission to update notation and replace $\CC\xT[t^{-1}]$ by $\Kinf$ as per your suggestion Joel?}
    % \jcom{Permission granted!}
    % \acom{replaced}

@@

\subsection{Some subvarieties of affine Grassmannians}
Now fix effective dominant weights $ \lambda_i,\mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sums $ \lambda = \lambda_1 + \lambda_2, \mu = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$. \acom{At some point at least mention that we expect this to go through for permutations of $\mu_i\in P_{++}$ i.e.\ skew partitions? or non-dominant, but also non-negative weights, so long as $\mu_1 + \mu_2$ is in $P_{++}$}

\acom{We will write only coset representatives for (orbits of) elements of the various Grassmannians; right cosets will be clear from context.}

% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
    % In the lattice model, we have %  G(\cO); understood from context 
    $$ 
    L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
    $$ 
    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
    \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
    % 
    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$. 
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}

@@

% $\begin{pNiceArray}{CC|CC}[first-row,last-row=5,first-col,last-col,nullify-dots]
% & C_1 & \Cdots & & C_4 & \\
% L_1 & a_{11} & a_{12} & a_{13} & a_{14} & L_1 \\
% \Vdots & a_{21} & a_{22} & a_{23} & a_{24} & \Vdots \\
% \hline
% & a_{31} & a_{32} & a_{33} & a_{34} & \\
% L_4 & a_{41} & a_{42} & a_{43} & a_{44} & L_4 \\
% & C_1 & \Cdots & & C_4 &
% \end{pNiceArray}$
\[
        A = \begin{bNiceArray}{ccc|ccc}[columns-width = auto,first-row,last-col,code-for-first-row = \color{blue}\scriptstyle\rotate,code-for-last-col = \color{blue}\scriptstyle,nullify-dots,xdots/line-style=loosely dotted]
        1 & \Cdots & \lambda_1 & \lambda_1 + 1 & \Cdots & \lambda_1 + \lambda_2 \\
        0 & 1 & 0 & 0 & 0 & 0 & 1\\
        0 & \Ddots & 1 & 0 & 0 & 0 & \Vdots \\
        0 & 0 & 0 & 1 & 0 & 0 & \lambda_1 \\
        \hline
         & & & s & 1 & 0 & \lambda_1 + 1 \\
         & & & 0 & \Ddots & 1 & \Vdots \\
         & & & 0 & 0 & s & \lambda_1 + \lambda_2 
        \end{bNiceArray} 
\]
% Denote by $R_i$ the $i$th row of $J$ 
Let $g = E_{\lambda_2}\cdots E_1$ be the product of elementary matrices $E_i$ which correspond to the elementary row operations 
$$R_{\lambda_1 + i - 1} \leftarrow R_{\lambda_1 + i-1} + \frac 1s R_{\lambda_1 + i}$$ 
for $i = 1,\dots,\lambda_2$. Then $gJg^{-1} = A$. For the next part we introduce the notation $A_{\lambda_1+\lambda_2}$ for this matrix $A$.

>>>>

Given a coweight $\mu \in P$ and $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix 
% with entries $ (t-s)^{\mu_1}, \dots, (t-s)^{\mu_m}$
% \[
%     \begin{pNiceMatrix}[nullify-dots,xdots/line-style=loosely dotted]
%         (t-s)^{\mu_1} & 0             & \Cdots & 0 \\
%         0             & (t-s)^{\mu_2} & \Ddots & \Vdots \\
%         % 0 & b & a & \Ddots & & \\
%         \Vdots              & \Ddots        & \Ddots & 0 \\
%         % \Vdots & & & & \\
%         0             & \Cdots        &   0    & (t-s)^{\mu_m}
%     \end{pNiceMatrix}
% \]
\[
\begin{bmatrix}
    (t-s)^{\mu_1} \\
    & (t-s)^{\mu_2} \\ 
    & & \ddots \\
    & & & (t-s)^{\mu_m}
\end{bmatrix} 
\]
which we will view in $\GL_m(K) $ for any ring $ K $ containing $\CC[t]$ in which $t-s$ is invertible (for example $ K = \Ks, \CC(t)$). % A: Think R sb K; changed it 
\acom{Add: Warning: We will also view $(t-s)^\mu$ in $\GL_m(K)/\GL_m(R)$. We hope it will be expedient and evident.}

@@

\subsection{Affine Grassmannians} %  actors
% To map thick Gr to C is to map a lattice to the points where it isn't trivialzable; doesn't make sense to ask for poles 
% G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
Set $\AA = \AA^1$ \acom{and let $V_0$ denote the trivial vector bundle}.

\jcom{I don't think that we need all this about ``formal disc centered at $s$'' below since we now define this in the rings and discs section.}
\acom{Ok. We could omit the repetitive $X=$ bits from the display styled alternate descriptions. That way they will fit within the margins.}

\begin{itemize}
    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by 
    $$
    \Gr = \left\{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0 \setminus \{0\} $} \right\} \,. 
    $$
    % where $V_0$ is the trivial rank $m$ vector bundle.
    % and $ D_0$ is the formal disc centered at $ 0 \in \PP$.

    We also have a lattice description 
    $$ 
    \Gr = \left\{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \right\}\,.
    $$
    % 
    \item For any $ s \in \CC $, 
    % \acom{should it be $\AA$ instead of $\CC$} 
    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
    $$
    \Gr_s = \left\{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_s \setminus \{s\} $} \right\}\,.
    $$
    % where $D_s$ is the formal disc centered at $s$ viewed as an element of $\PP$.
    % \acom{What about fixing the notation $V_0$ somewhere?}

    We also have a lattice description 
    $$ 
    \Gr_s = \left\{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \right\} \,. 
    $$   
    \item The thick affine Grassmannian $\Grth = G(\Kinf)/G(\CC[t])$. % \CC\xT[t^{-1}]
    It is described in modular terms by
    $$
        \Grth = \left\{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \right\}\,. % (a disc centered at $ \infty$)
    $$
    % where $D_\infty$ denotes a disc centered at $ \infty$. 
    % \acom{What is the difference between ``a disc'' and ``the formal disc''} \jcom{No difference.}

    We also have a lattice description 
    $$ 
    \Grth = \left\{ L \subset  \Kinf^m : \text{ $L$ is a $\CC[t]$-lattice} \right\}\,.
    $$ % \CC\xT[t^{-1}]^m

@@

    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
    It is described in modular terms by
    % {\small
    $$
    \Grbd = 
    % \begin{aligned}
        \left\{ 
            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \xrightarrow{\sim} V_0 \text{ on } \PP \setminus \{0, s\}  
        \right\} 
    % \end{aligned}
    $$%}
    % 
    The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by \rcom{why do we have the $s\ne 0$ restriction here}
    % 
    $$ 
    \Gr_{0,s} = G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
    $$
    % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
    % \jcom{Yes, that is one reason.  But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).  For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
    % \acom{lol}

    We also have a lattice descriptions 
    % {\small
    \begin{gather*}
    \Grbd = 
    \{ (L,s) :
    % s\in\AA,\,
    % L \subset  \CC(t)^m, s \in \AA 
    \text{$L \subset  \CC(t)^m$ is a $\CC[t]$-lattice trivial at any $ a \ne 0, s$} \} \\
    % , $L$ is 
     \Gr_{0,s} = 
    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}
    \end{gather*}%}
    \acom{We do not consistently specify where $s$ is in these definitions}
    % \acom{$s\in\CC$ should be $s\in\AA$?}
    % \jcom{Sorry I was very consistent about $ \CC$ vs $\AA$.  Which do you prefer?}
    % 
    \item The positive parts, $ \Gr^+$ and ${\Grth}^+$, of the affine Grassmannian and the thick affine Grassmannian, respectively, are defined as 
    % and of the thick affine Grassmannian ${\Grth}^+$ is defined as
    $$
    \Gr^+ = \left(M_m(\cO) \cap G(\cK)\right) / G(\cO) \text{ and } {\Grth}^+ = \left(M_m(\CC[t]) \cap G(\Kinf)\right) / G(\CC[t])\,. % \CC\xT[t^{-1}] missed a spot  
    $$
    % \acom{What is $M_m$?} \jcom{The space of matrices.  I added it to the beginning of section 2.}
    % 
    In modular terms, $\Gr^+$ (resp. ${\Grth}^+$) is the set of those $ (V, \varphi)$ where $ \varphi : V \rightarrow V_0 $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp. over $ \PP$).

    In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the \acom{add (relevant)?} standard lattice. 
    % \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.  But I would like to leave the terminology ``trivial at $ a$'' is that ok, or should we write ``standard at $a$''.} 
    % \acom{Oh, I don't know.. is trivialized at $a$? is standardized at $a$? Maybe standard at $a$ is better.. Man I never thought about this interchangeable lingo.} 
    % lattice $ L_0(\cO)$ (resp. $L_0(\CC[t])$). % , i.e. $ L \subseteq L_0$.
\end{itemize}
% \acom{enumerate the points for now}
These different versions of the affine Grassmannian are related as follows.

\begin{enumerate}
    \item First there is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \cK \cong \Ks$.
    \item Second, we have a map from the two point BD affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
    % $$ \Grbd \rightarrow \Grth $$ 
    which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by \acom{...inclusion?}
    $$
    G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])\,. 
    $$
    % \acom{Permission to update notation and replace $\CC\xT[t^{-1}]$ by $\Kinf$ as per your suggestion Joel?}
    % \jcom{Permission granted!}
    % \acom{replaced}

@@

\subsection{Some subvarieties of affine Grassmannians}
Now fix effective dominant weights $ \lambda_i,\mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sums $ \lambda = \lambda_1 + \lambda_2, \mu = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$. 
% Coweights define elements in the various affine Grassmannians which we consider. Warning: We will write only coset representatives for elements of the various Grassmannians; we hope that it is evident which right cosets they represent. 
% the right cosets which they represent are clear from the context.

\acom{At some point at least mention that we expect this to go through for permutations of $\mu_i\in P_{++}$ i.e.\ skew partitions? or non-dominant, but also non-negative weights, so long as $\mu_1 + \mu_2$ is in $P_{++}$}
% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
    % In the lattice model, we have %  G(\cO); understood from context 
    $$ 
    L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
    $$ 
    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
    % 
    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$. 
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}

@@

% $\begin{pNiceArray}{CC|CC}[first-row,last-row=5,first-col,last-col,nullify-dots]
% & C_1 & \Cdots & & C_4 & \\
% L_1 & a_{11} & a_{12} & a_{13} & a_{14} & L_1 \\
% \Vdots & a_{21} & a_{22} & a_{23} & a_{24} & \Vdots \\
% \hline
% & a_{31} & a_{32} & a_{33} & a_{34} & \\
% L_4 & a_{41} & a_{42} & a_{43} & a_{44} & L_4 \\
% & C_1 & \Cdots & & C_4 &
% \end{pNiceArray}$
\begin{comment}
\[
        A = \begin{bNiceArray}{ccc|ccc}[columns-width = auto,first-row,last-col,code-for-first-row = \color{blue}\scriptstyle\rotate,code-for-last-col = \color{blue}\scriptstyle,nullify-dots,xdots/line-style=loosely dotted]
        1 & \Cdots & \lambda_1 & \lambda_1 + 1 & \Cdots & \lambda_1 + \lambda_2 \\
        0 & 1 & 0 & 0 & 0 & 0 & 1\\
        0 & \Ddots & 1 & 0 & 0 & 0 & \Vdots \\
        0 & 0 & 0 & 1 & 0 & 0 & \lambda_1 \\
        \hline
         & & & s & 1 & 0 & \lambda_1 + 1 \\
         & & & 0 & \Ddots & 1 & \Vdots \\
         & & & 0 & 0 & s & \lambda_1 + \lambda_2 
        \end{bNiceArray} 
\]
\end{comment}
% Denote by $R_i$ the $i$th row of $J$ 
Let $g = E_{\lambda_2}\cdots E_1$ be the product of elementary matrices $E_i$ which correspond to the elementary row operations 
$$R_{\lambda_1 + i - 1} \leftarrow R_{\lambda_1 + i-1} + \frac 1s R_{\lambda_1 + i}$$ 
for $i = 1,\dots,\lambda_2$. Then $gJg^{-1} = A$. For the next part we introduce the notation $A_{\lambda_1+\lambda_2}$ for this matrix $A$.
